Effects of Antenna Beam Chromaticity on Redshifted 21~cm Power Spectrum and Implications for Hydrogen Epoch of Reionization Array

### 2016-03-22 ForegroundSimulations/ms.tex
Change in author ordering, Abstract and Intro
From b8ea8c2 (fgsim):
====================

In ms.tex,

(*) Minor changes in Abstract and Introduction.
(*) Change in author ordering

%% Author list
\author{
%% Lead Authors
Nithyanandan~Thyagarajan\ASU\myemail,
Aaron~R.~Parsons\UCB,
David~R.~DeBoer\UCB,
Judd~D.~Bowman\ASU,
%% Co-authors
Nipanjana~Patra\UCB,
Aaron~M.~Ewall-Wice\MIT,
Abraham~R.~Neben\MIT
}

@@

Unaccounted systematics from foregrounds and instruments prevent current experiments from detecting redshifted 21~cm signal from the Epoch of Reionization (EoR). We identify spectral structures (chromaticity) in the antenna power pattern as one such systematic that significantly affects all EoR measurements. Increase in chromaticity of the antenna beam causes the already bright foreground power to leak well beyond ideal limits and contaminate the otherwise clean EoR signal modes. A primary source of this chromaticity is reflections in the antenna-feed assembly and between structures in neighboring antennas. Using precise foreground simulations taking wide-field effects into account, we provide a framework to set cosmologically-motivated design specifications on these reflections to prevent further EoR signal degradation. We use the Hydrogen Epoch of Reionization Array (HERA) as an example. Using a simple and yet high dynamic range spectral weighting scheme, we demonstrate that EoR detection using HERA will not be impeded by such spectral systematics even in a conservative scenario that does not perform removal of foregrounds. We also show that all baselines in a 19-element HERA layout are capable of detecting EoR over a substantial observing window on the sky.

@@

The Epoch of Reionization (EoR) is an important period of nonlinear growth of matter density perturbations and astrophysical evolution leading to the large scale structure observed currently in the Universe. The redshifted neutral hydrogen from the IGM in this epoch has been identified to be one of the most promising and direct probes of the EoR \citep{sun72,sco90,mad97,toz00,ili02}.

>>>>

%% Author list
\author{
%% Lead Authors
Nithyanandan~Thyagarajan\ASU\myemail,
Aaron~R.~Parsons\UCB,
David~R.~DeBoer\UCB,
Judd~D.~Bowman\ASU,
%% Co-authors
Aaron~M.~Ewall-Wice\MIT,
Abraham~R.~Neben\MIT,
Nipanjana~Patra\UCB
}

@@

Unaccounted systematics from foregrounds and instruments prevent current experiments from detecting redshifted 21~cm signal from the Epoch of Reionization (EoR). We identify spectral structures (chromaticity) in the antenna power pattern as one such systematic that significantly affects all EoR experiments. Increase in chromaticity of the antenna beam causes the already bright foreground power to leak well beyond ideal limits and contaminate the otherwise clean EoR signal modes. A primary source of this chromaticity is reflections in the antenna-feed assembly and between structures in neighboring antennas. Using precise foreground simulations taking wide-field effects into account, we provide a framework to set cosmologically-motivated design specifications on these reflections to prevent further EoR signal degradation. We use the Hydrogen Epoch of Reionization Array (HERA) as an example. Using a simple and yet high dynamic range spectral weighting scheme, we demonstrate that EoR detection using HERA will not be impeded by such spectral systematics even in a conservative scenario that does not perform removal of foregrounds. All baselines in a 19-element HERA layout are capable of detecting EoR over a substantial observing window on the sky.

@@

The Epoch of Reionization (EoR) is an important period of nonlinear growth of matter density perturbations and astrophysical evolution leading to the large scale structure observed currently in the Universe. The redshifted neutral hydrogen in this epoch has been identified to be one of the most promising and direct probes of the EoR \citep{sun72,sco90,mad97,toz00,ili02}.
